The problem and promise of scale in multilayer networks

### 2019-12-08 paper/introduction.Rmd
first paragraph

<!-- Landscape spatial scale -->

<!-- Social proximity scale -->

@@

<!-- Multilayer networks
used across disciplines
-->
Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a]. They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a]. Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].

@@

>>>>

<!-- Landscape spatial scale -->
Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992].

heteroneity of landscapes
within seemingly homogeneous patches, exist lower level processes including species interactions, resource availability, disease transfer [@legendre1993]

Animals may be influenced by processes at multiple scales

<!-- observational scales of landscapes do not necessarily correspond to the "scale of effect" of species-landscape relationships, or the scale at which there is the strongest relationship [@jackson2015]-->

the scales that influence animals and the patterns of their landscapes may be disjoint [@chave2013]. The effects of scale have been explicitly investigated across many ecological studies including habitat selection [@mayor2007], evaluating satellite imagery [@benson1995] and    of ecology including landscape ecology, movement ecology, earth observation [@benson1995], habitat selection[@mayor2007]

<!-- observers bias their perspective when selecting a scale,often unknowingly or without considering the implications [@allen2015].  -->

Scale can be considered for all measured quantities [@schneider2009] including spatial and temporal variables as well as domain specific <!--lead into social-->

<!-- Social proximity scale 
sociality exists 
-->
Social scale is the type of social relationship measured and how this relationship is defined [@farine2015]. If the greater range of a social relationship is the entire social system for an organism, a particular social scale may focus on only a limited type of relationship like grooming or aggression.

@@

<!-- Multilayer networks
used across disciplines
-->
Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a]. They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a]. <!--GENERALLY INTERESTING Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].-->

For multilayer social networks, three types of scale are relevant: spatial, temporal and social scale.

@@

integrating networks across scales
explore sensitivity of network measures to scale
